Perihelion advance of Mercury

### 2020-10-07 perihelion_advance_of_mercury.Rmd
typo

From the above we see that the trajectory has been simulated up to
about $965$ radians or about $\frac{965}{2\pi}\simeq 153$ revolutions
round the sun.  Plotting the entire trajectory is computationally
expensive, but we can plot the simulated trajectory close to aphelion
as for the Newtonian case:

>>>>

From the above we see that the trajectory has been simulated up to
about $965$ radians or about $\frac{965}{2\pi}\simeq 153$ revolutions
round the sun.  Plotting the entire trajectory is computationally
expensive, but we can plot part of the simulated trajectory close to
aphelion as for the Newtonian case:
